Estimating Planetary Habitability via Particle Swarm Optimization of CES Production Functions.

### 2018-01-18 docs/report/report.tex
Fixed an issue with the Bibliography.

\documentclass[10pt,draft]{article}

@@

\usepackage[title]{appendix}
\usepackage{booktabs}
\usepackage{enumitem}

@@

\textcite{Cop} describe a way to represent non-strict inequality constraints when optimizing using a particle swarm.
Strict inequalities and equality constraints need to be converted to non-strict inequalities before being represented in
the problem. Introducing an error threshold $\epsilon$ converts strict inequalities of the form ${g_k}^{\prime}(x) < 0$
to non-strict inequalities of the form $g_k(x) = {g_k}^{\prime}(x) + \epsilon \leq 0$. A tolerance $\tau$ is used to
transform equality constraints to a pair of inequalities,
\begin{equation*}
  \begin{aligned}
    g_{(q+l)}(x) &= h_l(x) - \tau \leq 0,&&\quad l = 1\dots r\,,\\
    g_{(q+r+l)}(x) &= {-}h_l(x) - \tau \leq 0,&&\quad l = 1\dots r\,.
  \end{aligned}
\end{equation*}
% Cite: PSO Constraints paper.
Thus, $r$ equality constraints become $2r$ inequality constraints, raising the total number of constraints to $s = q +
2r$. For each solution $p_i$, $c_i$ denotes the constraint vector where, $c_{ik} = \max\{g_k(p_i), 0\},~k=1\dots s$.
When $c_{ik} = 0,~\forall k=1\dots s$, the solution $p_i$ lies within the feasible region. When $c_{ik} > 0$, the
solution $p_i$ violates the $k$\tsup{th} constraint.

@@

% Cite data set.
The data set used for estimating the Habitability Scores of exoplanets, described in Section~\ref{sec:habscore}, was the
Confirmed Exoplanets Catalog maintained by the Planetary Habitability Laboratory (PHL). The catalog records observed and
modeled parameters for exoplanets confirmed by the Extrasolar Planets Encyclopedia. Table~\ref{tab:param} describes the
parameters from the PHL Exoplanets Catalog (PHL-EC) used for the experiment. Since surface temperature and eccentricity
are not recorded in Earth Units, we normalized these values by dividing them with Earth's surface temperature
(\SI{288}{\kelvin}) and eccentricity (\num{0.017}). PHL-EC assumes an Eccentricity of 0 when unavailable. The PHL-EC
records empty values for planets whose surface temperature is not known. We chose to drop these records from the
experiment.

@@

  Matrices $P$ and $V$ represent current position and velocity of all particles in the swarm.
  \begin{alignat}{2}
    P &= [\ p_{ij}\ &&\mid\ \forall i=1\dots n,\;\forall j=1\dots d\ ]\,,\\
    V &= [\ v_{ij}\ &&\mid\ \forall i=1\dots n,\;\forall j=1\dots d\ ]\,.
  \end{alignat}
  $p_{ij}$ and $v_{ij}$ denote position and velocity of particle $i$ in dimension $d$. Matrices $B$ and $L$ represent
  the $\pbest$ and $\lbest$ values for the swarm, where,
  \begin{align}
    B &= [\ {\pbest}_i\ \mid\ \forall i=1\dots n\ ]\,,\\
    L &= [\ \argmin_{B_j,\ j = 1\dots n} {\|B_j - P_i\|}^2\ \mid\ \forall i=1\dots n\ ]\,.
  \end{align}
  Section~\ref{sec:rep} outlined the use of a constraint vector for describing the feasibility of a solution. This
  concept generalizes to a matrix $C$, where,
  \begin{equation}
    C = [\ c_{ij}\ \mid\ \forall i=1\dots n,\;\forall j=1\dots s\ ]\,.
  \end{equation}
  Let $r',r''$ be two random vectors of length $n$ drawn from the uniform distribution ${U(0,1)}^n$. We use the
  shorthand notation of $X_i$ to denote the $i$\tsup{th} row of some matrix $X$. If $f(X_i)$ is the fitness function and
  $\mathit{constraints}(X)$ constructs $C$ for solutions $X$, the implementation of each iteration while updating
  particles in Algorithm~\ref{alg:cop} reduces to,
  \begin{align}
    V  =&\ \omega.V + \lambda_g\begin{bmatrix}
      {r_1}'(\gbest - P_1)\\
      {r_2}'(\gbest - P_2)\\
      \vdots\\
      {r_n}'(\gbest - P_n)
    \end{bmatrix} + \lambda_p\begin{bmatrix}
      {r_1}''(L_1 - P_1)\\
      {r_2}''(L_2 - P_2)\\
      \vdots\\
      {r_n}''(L_n - P_n)
    \end{bmatrix}\\
    V  =&\ \left[\ \sgn(v_{ij})*\max\{|v_{max}|,|v_{ij}|\}\ \mid\ \forall i=1\dots n,\;\forall j=1\dots d\ \right]\\
    P  =&\ P + V\\
    C  =&\ \mathit{constraints}(P)\\
    B  =&\ [\ X_i\ \mid\ (\textstyle\sum_{j=1}^s c_{ij} = 0 \to X_i = \argmax\{f(P_i), f(B_i)\})\ \wedge\\
        &\qquad(\textstyle\sum_{j=1}^s c_{ij} \neq 0 \to X_i = B_i),\ \forall i=1\dots n\ ]\\
    \gbest =&\ \argmax_{{B}_i} \{\ {f(B_i)}\ \mid\ \forall i=\dots n\ \}
  \end{align}

>>>>

\documentclass[10pt]{article}

@@

\usepackage[title]{appendix}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{enumitem}

@@

\textcite{Cop} describe a way to represent non-strict inequality constraints when optimizing using a particle swarm.
Strict inequalities and equality constraints need to be converted to non-strict inequalities before being represented in
the problem. Introducing an error threshold $\epsilon$ converts strict inequalities of the form ${g_k}^{\prime}(x) < 0$
to non-strict inequalities of the form $g_k(x) = {g_k}^{\prime}(x) + \epsilon \leq 0$. A tolerance $\tau$ is used to
transform equality constraints to a pair of inequalities,
\begin{equation*}
  \begin{aligned}
    g_{(q+l)}(x) &= h_l(x) - \tau \leq 0,&&\quad l = 1\dots r\,,\\
    g_{(q+r+l)}(x) &= {-}h_l(x) - \tau \leq 0,&&\quad l = 1\dots r\,.
  \end{aligned}
\end{equation*}
Thus, $r$ equality constraints become $2r$ inequality constraints, raising the total number of constraints to $s = q +
2r$. For each solution $p_i$, $c_i$ denotes the constraint vector where, $c_{ik} = \max\{g_k(p_i), 0\},~k=1\dots s$.
When $c_{ik} = 0,~\forall k=1\dots s$, the solution $p_i$ lies within the feasible region. When $c_{ik} > 0$, the
solution $p_i$ violates the $k$\tsup{th} constraint.

@@

The data set used for estimating the Habitability Scores of exoplanets, described in Section~\ref{sec:habscore}, was the
Confirmed Exoplanets Catalog maintained by the Planetary Habitability Laboratory (PHL)~\cite{PHL}. The catalog records
observed and modeled parameters for exoplanets confirmed by the Extrasolar Planets Encyclopedia. Table~\ref{tab:param}
describes the parameters from the PHL Exoplanets Catalog (PHL-EC) used for the experiment. Since surface temperature and
eccentricity are not recorded in Earth Units, we normalized these values by dividing them with Earth's surface
temperature (\SI{288}{\kelvin}) and eccentricity (\num{0.017}). PHL-EC assumes an Eccentricity of 0 when unavailable.
The PHL-EC records empty values for planets whose surface temperature is not known. We chose to drop these records from
the experiment.

@@

  Matrices $P$ and $V$ represent current position and velocity of all particles in the swarm.
  \begin{alignat*}{2}
    P &= [\ p_{ij}\ &&\mid\ \forall i=1\dots n,\;\forall j=1\dots d\ ]\,,\\
    V &= [\ v_{ij}\ &&\mid\ \forall i=1\dots n,\;\forall j=1\dots d\ ]\,.
  \end{alignat*}
  $p_{ij}$ and $v_{ij}$ denote position and velocity of particle $i$ in dimension $d$. Matrices $B$ and $L$ represent
  the $\pbest$ and $\lbest$ values for the swarm, where,
  \begin{align*}
    B &= [\ {\pbest}_i\ \mid\ \forall i=1\dots n\ ]\,,\\
    L &= [\ \argmin_{B_j,\ j = 1\dots n} {\|B_j - P_i\|}^2\ \mid\ \forall i=1\dots n\ ]\,.
  \end{align*}
  Section~\ref{sec:rep} outlined the use of a constraint vector for describing the feasibility of a solution. This
  concept generalizes to a matrix $C$, where,
  \begin{equation*}
    C = [\ c_{ij}\ \mid\ \forall i=1\dots n,\;\forall j=1\dots s\ ]\,.
  \end{equation*}
  Let $r',r''$ be two random vectors of length $n$ drawn from the uniform distribution ${U(0,1)}^n$. We use the
  shorthand notation of $X_i$ to denote the $i$\tsup{th} row of some matrix $X$. If $f(X_i)$ is the fitness function and
  $\mathit{constraints}(X)$ constructs $C$ for solutions $X$, the implementation of each iteration while updating
  particles in Algorithm~\ref{alg:cop} reduces to,

  \begin{align*}
    V  =&\ \omega.V + \lambda_g\begin{bmatrix}
      {r_1}'(\gbest - P_1)\\
      {r_2}'(\gbest - P_2)\\
      \vdots\\
      {r_n}'(\gbest - P_n)
    \end{bmatrix} + \lambda_p\begin{bmatrix}
      {r_1}''(L_1 - P_1)\\
      {r_2}''(L_2 - P_2)\\
      \vdots\\
      {r_n}''(L_n - P_n)
    \end{bmatrix}\\
    V  =&\ \left[\ \sgn(v_{ij})*\max\{|v_{max}|,|v_{ij}|\}\ \mid\ \forall i=1\dots n,\;\forall j=1\dots d\ \right]\\
    P  =&\ P + V\\
    C  =&\ \mathit{constraints}(P)\\
    B  =&\ [\ X_i\ \mid\ (\textstyle\sum_{j=1}^s c_{ij} = 0 \to X_i = \argmax\{f(P_i), f(B_i)\})\ \wedge\\
        &\qquad(\textstyle\sum_{j=1}^s c_{ij} \neq 0 \to X_i = B_i),\ \forall i=1\dots n\ ]\\
    \gbest =&\ \argmax_{{B}_i} \{\ {f(B_i)}\ \mid\ \forall i=\dots n\ \}
  \end{align*}
